\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}

\begin{document}
\name{\Large George WP Horrell}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    Phone: (650) 391-7452       \hfill LinkedIn: \url{https://www.linkedin.com/in/georgewphorrell} \\
    \noindent Email: ghorrell@stanford.edu  \hfill GitHub: \url{http://github.com/georgehorrell} \vspace{0mm}\\\vspace{-4.5mm}

    \section{\mysidestyle Education}

    \textbf{Stanford University}, Stanford, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{B.Sc., Computer Science} \hfill \textbf{Sep 2015 -- Jul 2019}\\
    Class of 2019. GPA currently standing at 3.8. Studying the artificial intelligence track.

    \section{\mysidestyle Experience}
    
    \textbf{Airbnb}, San Francisco, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineering Intern} \hfill \textbf{Jun 2018 --}
    \begin{itemize}
	\setlength\itemsep{-0.05em}
        \item Working on the infrastructure team.
	\end{itemize}
    
    \textbf{Axon}, Seattle, WA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineering Intern} \hfill \textbf{Jul 2017 - Sep 2017}
    \begin{itemize}
	\setlength\itemsep{-0.05em}
        \item Focus on full-stack development, gaining proficiency in React, Redux and Scala. 
	    \item Developed a web-view visualization designed to indicate the relative duration of events that occur during a police officer's shift.
        \item Aided changeover to new guidelines for frontend development through component refactoring.
	\end{itemize}
    
    \textbf{Stanford University}, Stanford, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{CS198 Section Leader} \hfill \textbf{Dec 2016 --}
    \begin{itemize}
	\setlength\itemsep{-0.05em}
 	    \item Leading sections of eight to ten people: teaching introductory computer science.
        \item Teaching basic proficiency in algorithms, data structures and complexity analysis.
	    \item Grading exams and assignments, holding office hours and encouraging extension work.
    \end{itemize}

    \textbf{Headstart App}, London, UK \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineering Intern} \hfill \textbf{Oct 2016 -- Dec 2016}
    \begin{itemize}
	\setlength\itemsep{-0.05em}
        \item Front-end development with Feathers, Mongoose \& React.
    \end{itemize}

    \textbf{Arcadis}, London, UK \vspace{2mm}\\\vspace{1mm}%
    \textsl{Management Consultant Intern} \hfill \textbf{Dec 2014 -- May 2015}
    \begin{itemize}
	\setlength\itemsep{-0.05em}
        \item Presented to senior members of large multinational client, focusing on whole business projection.
        \item Developed an algorithm that linked desired output of vehicles with property infrastructure.
    \end{itemize}

   \section{\mysidestyle Projects}
   
    \textbf{BoneNet} \vspace{2mm}\\\vspace{1mm}%
   	\textsl{Stanford Artificial Intelligence in Medical Imaging} \hfill \textbf{Jun 2018 -- Sep 2018}\\
    Developed machine learning techniques for classifying lower body X-Ray extremity abnormalities.
    \begin{itemize}
	\setlength\itemsep{-0.05em}
        \item Problem assigned involved classified cases of multiple X-Rays as displaying an abnormality.
        \item Acted as team leader for group of three undergraduates.
        \item Researched and developed multiple instance learning methods, including Attention with convolutional networks and recurrent convolution neural networks.
    \end{itemize}

    \textbf{An AI Agent for Playing Hex} \vspace{2mm}\\\vspace{1mm}%
    \textsl{CS221 Project} \hfill \textbf{May 2016 -- Dec 2016}\\
    Created an agent for the abstract strategy game of Hex as part of a team of three.
    \begin{itemize}
	\setlength\itemsep{-0.05em}
    	\item Developed multiple algorithms for move selection, including Minimax, Beam Search and Monte Carlo Tree Search (MCTS).
        \item Personally ported the project from Python to C++, yielding our most performant agent, running the MCTS-Rave algorithm at a high number of iterations.
    \end{itemize}
    
    \textbf{Politronix}, politronix.com \vspace{2mm}\\\vspace{1mm}%
    \textsl{Cofounder - Full Stack Development} \hfill \textbf{May 2016 -- Dec 2016}\\
    Lead front end development for a political sentiment analysis tool. Politronix runs sentiment analysis on twitter posts related to candidates in the 2016 presidential election. Contributions include:
    \begin{itemize}
	\setlength\itemsep{-0.05em}
        \item Created a full stack framework for serving live data on Node.js with Plot.ly.
        \item Integrated Twitter streaming API interface and database schemas.
    \end{itemize}

    \section{\mysidestyle Skills}

    \emph{Experienced Programming:} Python, C, C++, React, Redux, CSS, Node.js, Java \\
    \emph{Basic Programming:} MySQL, Android, \LaTeX, Keras, Tensorflow, Scala
\end{resume}
\end{document}
